First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-15 eg6-letters/coherent/dvcs_he4_prl.tex
alpha0->alpha1 in sensitivity discussion

The results in Figure \ref{fig:CFF_HA} show that the extraction of the CFF
from the beam spin asymmetry is possible without any model dependent 
assumptions. The amplitude and the dependencies observed as a function of 
$Q^{2}$, $x_B$, and $-t$ are in agreement 
with the theoretical expectations. One can see a difference between the 
precision of the extracted imaginary and real parts, which is expected from
Eq.~\ref{eq:A_LU-coh} because $\alpha_2$ is smaller than $\alpha_0$. While the 
accuracy of our results does not allow to discriminate between the models, they 
demonstrate possibility of extraction of the CFF of spin 0 target in a model 
independent way.

>>>>

The results in Figure \ref{fig:CFF_HA} show that the extraction of the CFF
from the beam spin asymmetry is possible without any model dependent 
assumptions. The amplitude and the dependencies observed as a function of 
$Q^{2}$, $x_B$, and $-t$ are in agreement 
with the theoretical expectations. One can see a difference between the 
precision of the extracted imaginary and real parts, which is expected from
Eq.~\ref{eq:A_LU-coh} because $\alpha_2$ is much smaller than $\alpha_1$. While the 
accuracy of our results does not allow to discriminate between the models, they 
demonstrate possibility of extraction of the CFF of spin 0 target in a model 
independent way.
